### 2019-11-25 monograph/chapters/object_beautifier.tex
Added new languages scopes to object_beautifier.tex example

\lstset{xleftmargin=2em,aboveskip=0pt}
\begin{lstlisting}[caption={Exemplo de Gramática Utilizada pelo Formatador de Código},label={exemploDeGramaticaUtilizada},style=yaml_style]
scope: source.sma
name: Abstract Machine Language
contexts: {
    match: if\( {
        scope: if.statement.definition
        push: {
            meta_scope: if.statement.body
            match: \) {
                scope: if.statement.definition
                pop: true
            }
        }
    }
}
\end{lstlisting}

>>>>

\lstset{xleftmargin=2em,aboveskip=0pt}
\begin{lstlisting}[caption={Exemplo de Gramática Utilizada pelo Formatador de Código},label={exemploDeGramaticaUtilizada},style=yaml_style]
scope: source.sma source.c++ source.javascript source.rust
name: Abstract Machine Language
contexts: {
    match: if\( {
        scope: if.statement.definition
        push: {
            meta_scope: if.statement.body
            match: \) {
                scope: if.statement.definition
                pop: true
            }
        }
    }
}
\end{lstlisting}
